Drake Plan

### 2019-08-19 AOD_CONUS_Report.Rmd
the version that run 30days model

```{r}
library(drake)

@@

@@

```{r}

readd(plotSHAP1_2, cache = ssd_cache)

@@

```{r}
readd(print1_2, cache = ssd_cache)
readd(plot1_2, cache = ssd_cache)

@@

```{r}
readd(plotSHAP1_2, cache = ssd_cache)

@@

>>>>

```{r}
library(drake) 
loadd(plotAOD, cache = ssd_cache)
n_vars = length(plotAOD)
fig_height = ceiling(n_vars/2)*3.5
```

# AOD Scatterplot

```{r, fig.width = 10, fig.height = fig_height}
loadd(plotAOD, cache = ssd_cache)
gridExtra::grid.arrange(grobs = plotAOD, ncol = 2)
```

@@

## RMSE

@@

## Scatterplot

```{r, fig.width = 10, fig.height = fig_height}
loadd(plotscatter, cache = ssd_cache)
gridExtra::grid.arrange(grobs = plotscatter, ncol = 2)
```

## SHAP

```{r}
readd(plotSHAP1, cache = ssd_cache)
```

```{r, fig.width = 10, fig.height = fig_height}
loadd(plotSHAP2, cache = ssd_cache)
gridExtra::grid.arrange(grobs = plotSHAP2, ncol = 2)
```

@@

## RMSE

```{r}
readd(print1_2, cache = ssd_cache)
readd(plot1_2, cache = ssd_cache)
```

@@

## Scatterplot

```{r, fig.width = 10, fig.height = fig_height}
loadd(plotscatter_2, cache = ssd_cache)
gridExtra::grid.arrange(grobs = plotscatter_2, ncol = 2)

@@

## SHAP

```{r}
readd(plotSHAP1_2, cache = ssd_cache)
```

```{r, fig.width = 10, fig.height = fig_height}
loadd(plotSHAP2_2, cache = ssd_cache)
gridExtra::grid.arrange(grobs = plotSHAP2_2, ncol = 2)

### 2019-08-19 R/drake_plan_conus.Rmd
the version that run 30days model

# for reporting purpose
y_var = "diff_AOD"
y_var_pred = "diff_AOD_pred"

@@

  # select aer sites in mcd19. further limit the stations
  sel_aer = target(aer_in_mcd19(aer_nearest_2, mcd19 = join),
             transform = map(join)),
  # buffers 
  ref = target(ref_in_buffer(region_aer_m = sel_aer, refgrid),
             transform = map(sel_aer)),
  # sites
  p = target(get_site_list(region_aer_m = sel_aer), transform = map(sel_aer)),
  n = target(get_site_name(region_aer_m = sel_aer), transform = map(sel_aer)),

@@

  # 6. Report -----------------------------------------------------------
  print1 = target(report_rmse(cv_results),
                  transform = map(cv_results,.id = FALSE)),
  plot1 = target(plot_rmse(cv_results),
                 transform = map(cv_results,.id = FALSE)),
  plotSHAP1 = target(plot_SHAP(cv_results),
                 transform = map(cv_results,.id = FALSE)),
  report = rmarkdown::render(
    knitr_in("AOD_CONUS_Report.Rmd"),
    output_file = file_out("AOD_CONUS_Report.html"))
)
nemia_plan
#drake_plan_source(nemia_plan)
nemia_config <- drake_config(nemia_plan, cache = ssd_cache) # show the dependency
# vis_drake_graph(nemia_config, from = names(nemia_config$layout))
vis_drake_graph(nemia_config, ncol_legend = 0)

>>>>

# for reporting purpose
y_var = "diff_AOD"
y_var_pred = "diff_AOD_pred"
# how many features to print in scatterplot
n_vars = 4

@@

  # select aer sites in mcd19. further limit the stations
  sel_aer = target(aer_in_mcd19(aer_nearest_2, mcd19 = join),
             transform = map(join)),
  # buffers 
  ref = target(ref_in_buffer(sel_aer, refgrid),
             transform = map(sel_aer)),
  # sites
  p = target(get_site_list(region_aer_m = sel_aer), transform = map(sel_aer)),
  n = target(get_site_name(region_aer_m = sel_aer), transform = map(sel_aer)),

@@

  # 6. Report -----------------------------------------------------------
  print1 = target(report_rmse(cv_results),
                  transform = map(cv_results,.id = FALSE)),
  plot1 = target(plot_rmse(cv_results),
                 transform = map(cv_results,.id = FALSE)),
  # figures
  plotAOD = target(plot_AOD(cv_results),
                 transform = map(cv_results,.id = FALSE)),
  plotscatter = target(plot_scatter(cv_results),
                 transform = map(cv_results,.id = FALSE)),

  shap_long = target(get_SHAP_long(cv_results),
                  transform = map(cv_results,.id = FALSE)),
  plotSHAP1 = target(plot_SHAP(shap_long),
                 transform = map(shap_long,.id = FALSE)),
  plotSHAP2 = target(plot_SHAP_scatter(cv_results, shap_long),
                 transform = map(cv_results, shap_long,.id = FALSE)),
  report = rmarkdown::render(
    knitr_in("AOD_CONUS_Report.Rmd"),
    output_file = file_out("AOD_CONUS_Report.html"))
)
nemia_plan
#drake_plan_source(nemia_plan)
nemia_config <- drake_config(nemia_plan, cache = ssd_cache) # show the dependency
# vis_drake_graph(nemia_config, from = names(nemia_config$layout))
vis_drake_graph(nemia_config, ncol_legend = 0)

make(nemia_plan, cache = ssd_cache)
```
